Project 2

### 2021-10-06 project_2.Rmd
All texts imported

```{r load_libraries}
#loading all the necessary libraries
library(gutenbergr)
library(tidytext)
library(tidyverse)

```

@@

>>>>

```{r load_libraries}
#loading all the necessary libraries
library(gutenbergr)
library(tidytext)
library(tidyverse)
library(vroom)
library(readtext)
```

@@

```{r import_Hemingway_books}

The_Sun_Also_Rises_Hemingway_Ernest <- read_delim("The Sun Also Rises_Hemingway, Ernest.txt", 
    delim = "\t", quote = "\\\"", escape_double = FALSE, 
    trim_ws = TRUE)
The_Old_Man_and_the_Sea_Hemingway_Ernest <- read_delim("The Old Man and the Sea_Hemingway, Ernest.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
For_Whom_the_Bell_Tolls_Hemingway_Ernest <- read_delim("For Whom the Bell Tolls_Hemingway, Ernest.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
A_Farewell_to_Arms_Hemingway_Ernest <- read_delim("A Farewell to Arms_Hemingway, Ernest.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
```

```{r import_Hemingway_bulk}
#DO NOT RUN
file_list <- list.files(path = ".", recursive = FALSE, pattern = "*Ernest.txt$", full.names = FALSE)

Hemingway_files <- vroom(file_list, delim = ".", col_names = FALSE)
```

```{r hemingway_corpus}
#DO NOT RUN
DATA_DIR <- "."
hemingway_corpus <- readtext("A Farewell to Arms_Hemingway, Ernest.txt", docvarsfrom = "filenames", docvarnames = c("title", "author"), devsep = "_")
```
